---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/R Saves Semester 3/Assignment 4")
library(crqa); library(tseriesChaos); library(nonlinearTseries); library(SparseM); library(lme4); library(dplyr); library(lmerTest); library(MuMIn); library(caret); library(pROC); library(groupdata2); library(ggplot2); library(gridExtra)
library(stringr)
```

```{r}
#Choose one pair - group 8 and load the data
turn = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/CleanData/Study2_G8_T1_TurnTaking.csv")

sync = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/CleanData/Study2_G8_T2_Synchronous.csv")

conv = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/CleanData/Study2_G8_T3_Conversation.csv")
```


## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?

```{r}
#Downsampling
conv = conv %>%
    groupdata2::group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

sync = sync %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

turn = turn %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

```


```{r}
#Plots for respiration
respconv = ggplot(conv,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respconv")

respsync = ggplot(sync,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respsync")

respturn = ggplot(turn,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title = "respturn")

#Plots for HR
hrconv = ggplot(conv,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrconv")

hrsync = ggplot(sync,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrsync")

hrturn = ggplot(turn,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrturn")

#Show the plots together
group8 = grid.arrange(respconv, respsync, respturn, hrconv, hrsync, hrturn , ncol=3)

```

```{r}
#Remove outliers, 2.5 has turned out to be a good threshold according to Riccardo's trial and error

removeOuts <- function(ts,threshold){
   ts[ts > (mean(ts,na.rm=T) +  
           (threshold*sd(ts,na.rm=T))) | 
        ts < (mean(ts,na.rm=T) -
           (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)  
return(ts)}

threshold=2.5

conv$HR1=removeOuts(conv$HR1,threshold)
conv$HR2=removeOuts(conv$HR2,threshold)
conv$Resp1=removeOuts(conv$Resp1,threshold)
conv$Resp2=removeOuts(conv$Resp2,threshold)
sync$HR1=removeOuts(sync$HR1,threshold)
sync$HR2=removeOuts(sync$HR2,threshold)
sync$Resp1=removeOuts(sync$Resp1,threshold)
sync$Resp2=removeOuts(sync$Resp2,threshold)
turn$HR1=removeOuts(turn$HR1,threshold)
turn$HR2=removeOuts(turn$HR2,threshold)
turn$Resp1=removeOuts(turn$Resp1,threshold)
turn$Resp2=removeOuts(turn$Resp2,threshold)

#Scale, subtract mean / sd
conv$Resp1=scale(conv$Resp1)  
conv$Resp2=scale(conv$Resp2)  
conv$HR1=scale(conv$HR1)
conv$HR2=scale(conv$HR2)
sync$Resp1=scale(sync$Resp1)  
sync$Resp2=scale(sync$Resp2)  
sync$HR1=scale(sync$HR1)
sync$HR2=scale(sync$HR2)
turn$Resp1=scale(turn$Resp1)  
turn$Resp2=scale(turn$Resp2)  
turn$HR1=scale(turn$HR1)
turn$HR2=scale(turn$HR2)

```

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.

```{r}
#Plots to see which should be excluded (group 1 and 2 at least for respiration data)

sync1 <- read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G1_T1_Synchronous.csv")

turn1 <- read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G1_T2_TurnTaking.csv")

turn2 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G2_T1_TurnTaking.csv")

sync2 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G2_T2_Synchronous.csv")

turn3 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G3_T2_TurnTaking.csv")

sync3 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study1_G3_T3_Synchronous.csv")


#Plots for respiration
respsync1 = ggplot(sync1,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respsync1")

respturn1 = ggplot(turn1,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respturn1")

respsync2 = ggplot(sync2,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respsync2")

respturn2 = ggplot(turn2,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respturn2")

respsync3 = ggplot(sync3,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respsync3")

respturn3 = ggplot(turn3,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respturn3")


#Plots for HR
hrsync1 = ggplot(sync1,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrsync1")

hrturn1 = ggplot(turn1,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrturn1")

hrsync2 = ggplot(sync2,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrsync2")

hrturn2 = ggplot(turn2,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrturn2")

hrsync3 = ggplot(sync3,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrsync3")

hrturn3 = ggplot(turn3,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="hrturn3")

#Show the plots together
group1 = grid.arrange(respsync1, respturn1, hrsync1, hrturn1, ncol=3)
group2 = grid.arrange(respsync2, respturn2, hrsync2, hrturn2, ncol=3)
group3 = grid.arrange(respsync3, respturn3, hrsync3, hrturn3, ncol=3)

#More plots ....
conv7 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study2_G7_T1_Conversation.csv")

sync7 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study2_G7_T2_Synchronous.csv")

turn7 = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/Study2_G7_T3_TurnTaking.csv")

respconv7 = ggplot(conv7,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respconv7")

respsync7 = ggplot(sync7,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respsync7")

respturn7 = ggplot(turn7,aes(time,Resp1))+geom_line()+geom_line(aes(time,Resp2),color="blue")+labs(title="respturn7")


HRconv7 = ggplot(conv7,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="HRconv7")

HRsync7 = ggplot(sync7,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="HRsync7")

HRturn7 = ggplot(turn7,aes(time,HR1))+geom_line()+geom_line(aes(time,HR2),color="blue")+labs(title="HRturn7")

group7 = grid.arrange(respconv7, respsync7, respturn7,HRconv7, HRsync7, HRturn7,ncol=3)
```


```{r}
removeOuts <- function(ts,threshold){
   ts[ts > (mean(ts,na.rm=T) +  
           (threshold*sd(ts,na.rm=T))) | 
        ts < (mean(ts,na.rm=T) -
           (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)  
return(ts)}

threshold=2.5

files = list.files(path = "~/Desktop/R Saves Semester 3/Assignment 4",pattern = "Study")

n = 1

for (i in files){

df = read.csv(i)

df = df %>%
    group(n = 100, method = 'greedy') %>%
    dplyr::summarise(
       time = mean(time,na.rm=T),
       HR1 = mean(HR1,na.rm=T),
       HR2 = mean(HR2,na.rm=T),
       Resp1 = mean(Resp1,na.rm=T),
       Resp2 = mean(Resp2,na.rm=T))

df$HR1=removeOuts(df$HR1,threshold)
df$HR2=removeOuts(df$HR2,threshold)
df$Resp1=removeOuts(df$Resp1,threshold)
df$Resp2=removeOuts(df$Resp2,threshold)

df$Resp1=scale(df$Resp1)  
df$Resp2=scale(df$Resp2)  
df$HR1=scale(df$HR1)
df$HR2=scale(df$HR2)

setwd("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data")
write.csv(df, file=i)
setwd("~/Desktop/R Saves Semester 3/Assignment 4")

}

n = n+1



```

- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

```{r}
#Riccardo's function
fitCrqa <- function(ts1,ts2){

par = list(lgM = 30, steps = seq(1, 6, 1), radiusspan = 100, radiussample = 100, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, fnnpercent = 10, typeami = "mindip")

Pars = try(optimizeParam(ts1, ts2, par, min.rec = 2, max.rec = 8))

if (length(Pars)>1){
Results=crqa(ts1, ts2, delay=Pars$delay, embed=Pars$emddim, radius=Pars$radius, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)
} else {
Results=NULL
Pars=NULL
Pars$delay=NA
Pars$emddim=NA
Pars$radius=NA
Results$RR=NA
Results$DET=NA
Results$maxL=NA
Results$L=NA
Results$ENTR=NA
Results$LAM=NA
Results$TT=NA
}

df=data.frame(Delay=Pars$delay,Embed=Pars$emddim,Radius=Pars$radius,RR=Results$RR,DET=Results$DET,LMAX=Results$maxL,L=Results$L,ENTR=Results$ENTR,LAM=Results$LAM,TT=Results$TT)

return(df)

}
```

```{r}
#Vores loop
setwd("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data")
files_preproc = list.files(path=".")

basic_df = NULL

n=1

for (i in files_preproc) {
  df = read.csv(i)
  resp_param = fitCrqa(df$Resp1,df$Resp2)
  HR_param = fitCrqa(df$HR1,df$HR2)
  df <- data.frame(respDelay = resp_param$Delay, respEmbed = resp_param$Embed,
  respRadius = resp_param$Radius, HRDelay = HR_param$Delay, HREmbed =
  HR_param$Embed, HRRadius = HR_param$Radius)
  
  if (exists("basic_df")) {
    basic_df = rbind(basic_df, df)
  } 
  else {
    basic_df = df
  }
  
  }
```

```{r}
#Use the few that worked to find optimal parameters
resp_delay = median(basic_df$respDelay,na.rm = TRUE)
resp_embed = median(basic_df$respEmbed,na.rm = TRUE)
resp_radius = median(basic_df$respRadius,na.rm = TRUE)

HR_delay = median(basic_df$HRDelay,na.rm = TRUE)
HR_embed = median(basic_df$HREmbed,na.rm = TRUE)
HR_radius = median(basic_df$HRRadius,na.rm = TRUE)

```


```{r}
setwd("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data")
files_preproc = list.files(path=".")

final_df = NULL

study = NULL
group = NULL
trial = NULL
condition = NULL

n=1

for (i in files_preproc) {
  
  study[n] = substr(i,6,6)
  group_temp = str_extract(i, "G\\d+")
  group[n] = str_extract(group_temp, "\\d")
  trial_temp = str_extract(i, "T\\d")
  trial[n] = str_extract(trial_temp, "\\d")
  condition_temp = str_extract(i, c("Turn", "Conv", "Sync"))
  condition[n] = na.omit(condition_temp)
  
  
  df = read.csv(i)
  
  results_resp = crqa (df$Resp1, df$Resp2, delay=resp_delay, embed=resp_embed, radius=resp_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

  results_HR = crqa (df$HR1, df$HR2, delay=HR_delay, embed=HR_embed, radius=HR_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)
  
  df <- data.frame(study = study[n], group = group[n], trial = trial[n], condition = condition[n], resp_RR = results_resp$RR, resp_DET = results_resp$DET, resp_NRLINE = results_resp$NRLINE, resp_maxL = results_resp$maxL, resp_L = results_resp$L, resp_ENTR = results_resp$ENTR, resp_rENTR = results_resp$rENTR, resp_LAM = results_resp$LAM, resp_TT = results_resp$TT, HR_RR = results_HR$RR, HR_DET = results_HR$DET, HR_NRLINE = results_HR$NRLINE, HR_maxL = results_HR$maxL, HR_L = results_HR$L, HR_ENTR = results_HR$ENTR, HR_rENTR = results_HR$rENTR, HR_LAM = results_HR$LAM, HR_TT = results_HR$TT)
  
 if (exists("final_df")) {
    final_df = rbind(final_df, df)
  } 
  else {
    final_df = df
    
  n = n + 1
  }
}

write.csv(final_df, file = "final_df")

```

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
 
```{r}
#Loop with shuffled files

setwd("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data")
files_preproc = list.files(path=".")

shuffle_df = NULL

study = NULL
group = NULL
trial = NULL
condition = NULL

n = 1

for (i in files_preproc) {
  
  study[n] = substr(i,6,6)
  group_temp = str_extract(i, "G\\d+")
  group[n] = str_extract(group_temp, "\\d")
  trial_temp = str_extract(i, "T\\d")
  trial[n] = str_extract(trial_temp, "\\d")
  condition_temp = str_extract(i, c("Turn", "Conv", "Sync"))
  condition[n] = na.omit(condition_temp)
  
  df = read.csv(i)
  
  df$HR1 <- sample(df$HR1)
  df$HR2 <- sample(df$HR2)
  df$Resp1 <- sample(df$Resp1)
  df$Resp1 <- sample(df$Resp2)
  
  
  results_resp = crqa (df$Resp1, df$Resp2, delay=resp_delay, embed=resp_embed, radius=resp_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

  results_HR = crqa (df$HR1, df$HR2, delay=HR_delay, embed=HR_embed, radius=HR_radius,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)
  
  df <- data.frame(study = study[n], group = group[n], trial = trial[n], condition = condition[n], resp_RR = results_resp$RR, resp_DET = results_resp$DET, resp_NRLINE = results_resp$NRLINE, resp_maxL = results_resp$maxL, resp_L = results_resp$L, resp_ENTR = results_resp$ENTR, resp_rENTR = results_resp$rENTR, resp_LAM = results_resp$LAM, resp_TT = results_resp$TT, HR_RR = results_HR$RR, HR_DET = results_HR$DET, HR_NRLINE = results_HR$NRLINE, HR_maxL = results_HR$maxL, HR_L = results_HR$L, HR_ENTR = results_HR$ENTR, HR_rENTR = results_HR$rENTR, HR_LAM = results_HR$LAM, HR_TT = results_HR$TT)
  
 if (exists("shuffle_df")) {
    shuffle_df = rbind(shuffle_df, df)
  } 
  else {
    shuffle_df = df
    
  n = n + 1
  }
}

write.csv(shuffle_df, file = "shuffle_df")
```

### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs
 
```{r}

wd = setwd("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data")
prepro_filelist = list.files(path=wd, pattern = "Study1") # load the preprocessed files

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

#!# temp info
#co = "Synchronous"
#i = 1
 
# Per each condition
for (co in c("Synchronous","TurnTaking")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study1_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study1_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2,Resp1S=d1$Resp1,Resp2S=d2$Resp2,HR1S=d1$HR1,HR2S=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2,Resp1S=d2$Resp1,Resp2S=d1$Resp2,HR1S=d2$HR1,HR2S=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1,Resp1S=d1$Resp1,Resp2S=d2$Resp1,HR1S=d1$HR1,HR2S=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2,Resp1S=d2$Resp2,Resp2S=d1$Resp2,HR1S=d2$HR2,HR2S=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write.csv(d3,file.path("surrogate",file3))
  write.csv(d4,file.path("surrogate",file4))
  write.csv(d5,file.path("surrogate",file5))
  write.csv(d6,file.path("surrogate",file6))
  }
}

##NOW DO THE SAME FOR STUDY 2##


```

### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?
 
```{r}
final_df = read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/final_df")

shuffle_df <- read.csv("~/Desktop/R Saves Semester 3/Assignment 4/Preproc_data/shuffle_df")

shuffle_df$typePairs <- "shuffled" 
final_df$typePairs <- "real"


shuffle_final_df <- rbind(final_df, shuffle_df)

model_resp_L <- lmer(resp_L~typePairs + trial + (1+trial|group), data = shuffle_final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
model_HR_L <- lmer(HR_L~typePairs + trial + (1+trial|group), data = shuffle_final_df, control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
summary(model_resp_L)
summary(model_HR_L)

resp_box <- ggplot(shuffle_final_df, aes(shuffle_final_df$typePairs, shuffle_final_df$resp_L)) + geom_point() + geom_boxplot() + labs(title = "Respiration data")

HR_box <- ggplot(shuffle_final_df, aes(shuffle_final_df$typePairs, shuffle_final_df$HR_L)) + geom_point() + geom_boxplot() + labs(title = "Heart rate data")

grid.arrange(resp_box,HR_box, ncol = 2)

cond_resp = ggplot(final_df, aes(x = final_df$condition, y = final_df$resp_L)) + geom_point() + geom_boxplot()+ labs(title = "Respiration data")


cond_HR = ggplot(final_df, aes(x = final_df$condition, y = final_df$HR_L)) + geom_point() + geom_boxplot()+labs(title = "Heart rate data")


grid.arrange(cond_resp,cond_HR, ncol = 2)

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them
 
```{r}

```

